\section{A}

% \begin{multicols}{2}

\entry{absence}{ab-sen-ce}{N-SING.}{The absence of something from a place is the fact that it is not there or does not exist.} ---~\textit{We present an approach for learning to translate an image from a source domain X to a target domain Y \textbf{in the absence of} paired examples.}


\entry{advance}{advance}{v.}{If you advance a cause, interest, or claim, you support it and help to make it successful.} ---~\textit{In particular, our model is capable of synthesizing 2K resolution videos of street scenes up to 30 seconds long, which significantly \textbf{advances} the state-of-the-art of video synthesis.}
 
 \entry{amenable}{amen-able}{adj.}{If you are amenable to something, you are willing to do it or accept it.} ---~\textit{We
find that applying orthogonal regularization to the generator renders it \textbf{amenable}...}

\entry{appealing}{appeal-ing}{adj.}{Someone or something that is appealing is pleasing and attractive.} ---~\textit{We observe that translations on training data are often more \textbf{appealing} than those on test data.}


\entry{approximately}{approximate-ly}{adv.} ---~\textit{One can \textbf{approximately} model all conditionals by training a family of conditional models that share parameters.}

\entry{aware}{aware}{adj.}{If you are aware of something, you know about it.} ---~\textit{We are not \textbf{aware} of any work making use of similarity metrics for machine learning, except a recent pre-print of Ridgeway et al. (2015).}






