\section{C}


\entry{chaotic}{chao-tic}{adj.}{Something that is chaotic is in a state of complete disorder and confusion.} --- \textit{This may be because minor structural errors are more visible in maps, which have rigid geometry, than in aerial photographs, which are more \textbf{chaotic}.}

\entry{compelling}{compel-l-ing}{adj.}{If you describe something such as a film or book, or someone's appearance, as compelling, you mean you want to keep looking at it or reading it because you find it so interesting.} --- \textit{The cGANs can produce \textbf{compelling} colorizations (first two rows), but have a common failure mode of producing a grayscale result (last row).}

\entry{complementary}{comple-ment-ary}{adj.}{Complementary things are different from each other but make a good combination.} --- \textit{ Further, we show that adaptation at both the pixel and representation level can offer \textbf{complementary} improvements with joint pixel-space and feature adaptation leading to the highest performing model for digit classification tasks.}


\entry{considerably}{consider-able-ly}{adv.}{Relatively or Pretty.} --- \textit{Here we show some of the most successful results in our test set - average performance is \textbf{considerably} worse.}

\entry{contemporary}{con-tempor-ary}{adj.}{Contemporary things are modern and relate to the present time.} --- \textit{Our experiments confirm that domain adaptation can benefit greatly from cycle-consistent pixel transformations, and that this is especially important for pixel-level semantic segmentation with \textbf{contemporary} FCN architectures.}


\entry{continuation}{continua-tion}{n.}{Something that is a continuation of something else is closely connected with it or forms part of it.} --- \textit{Like many deep generative models, GANs have previously been applied to semi-supervised learning [13, 14], and our work can be seen as a \textbf{continuation} and refinement of this effort.}

\entry{couple}{couple}{v.}{If you say that one thing produces a particular effect when it is coupled with another, you mean that the two things combine to produce that effect.} --- \textit{Through carefully-designed generator and discriminator architectures, \textbf{coupled} with spatio-temporal adversarial objective, we achieve high-resolution, photorealistic, temporally coherent video results on a diverse set of input formats including segmentation masks, sketches and poses.}

\entry{cumbersome}{cumbersome}{adj.}{A cumbersome system or process is very complicated and inefficient.} ---~\textit{Using a learned video synthesis model, one can generate realistic videos without explicitly specifying scene geometry, materials, lighting, and their dynamics, which would be \textbf{cumbersome} but necessary when using standard graphics rendering techniques.}


