\section{E}

\entry{eliminate}{eliminate}{vt.}{To eliminate something, especially something you do not want or need, means to remove it completely.} ---\textit{The fundamental improvement in
speed comes from \textbf{eliminating}  bounding box proposals and the subsequent pixel or feature resampling stage.}


\entry{elusive}{elusive}{adj.}{Something or someone that is elusive is difficult to find, describe, remember, or achieve.} ---\textit{Despite recent progress in generative image modeling, successfully generating high-resolution, diverse samples from complex datasets such as ImageNet remains
an \textbf{elusive} goal.}

\entry{encourage}{encourage}{vt.}{If something encourages a particular activity or state, it causes it to happen or increase.} --- \textit{We introduce the following techniques that are heuristically motivated to \textbf{encourage} convergence.}

\entry{engineer}{engine-er}{verb.}{When a vehicle, bridge, or building is engineered, it is planned and constructed using scientific methods.} ---\textit{We note that their method was specifically \textbf{engineered} to do well on colorization}

\entry{excel}{excel}{vi.}{If someone excels in something or excels at it, they are very good at doing it.} ---\textit{Deep neural networks \textbf{excel} at learning from large amounts of data, but can be poor at generalizing learned knowledge to new datasets or environments.}


\entry{explicit}{explicit}{adj.}{Something that is explicit is expressed or shown clearly and openly, without any attempt to hide anything.} ---\textit{
That is faster than
the previous state-of-the-art for single shot detectors (YOLO), and significantly
more accurate, in fact as accurate as slower techniques that perform \textbf{explicit} region
proposals and pooling (including Faster R-CNN).}

