\section{S}

\entry{sidestep}{side-step}{vt.}{If you sidestep a problem, you avoid discussing it or dealing with it.} --- \textit{We propose a new generative model estimation procedure that \textbf{sidesteps} these difficulties.}

\entry{spurious}{spur-ious}{adj.}{Something that is spurious seems to be genuine, but is false.} 
--- \textit{Even a slight departure from a network's training domain can cause it to make \textbf{spurious} predictions and significantly hurt its performance.}

\entry{striking}{strik-ing}{adj.}{Something that is striking is very noticeable or unusual.} --- \textit{So far, the most \textbf{striking} successes in deep learning have involved discriminative models, usually those that map a high-dimensional, rich sensory input to a class label.}

\entry{subtle}{subtle}{adj.}{Something that is subtle is not immediately obvious or noticeable.} 
--- \textit{In many cases, these modifications can be so \textbf{subtle} that a human observer does not even notice the modification at all, yet the classifier still makes a mistake.}

\entry{superior}{superior}{adj.}{If you describe something as superior, you mean that it is good, and better than other things of the same kind.} 
--- \textit{When both U-Net and encoder-decoder are trained with an L1 loss, the U-Net again achieves the \textbf{superior} results.}



\entry{surge}{surge}{n.}{A surge is a sudden large increase in something that has previously been steady, or has only increased or developed slowly.} 
--- \textit{Recently there has been a \textbf{surge} of interest in training neural networks to generate images.}


\entry{susceptible}{suscepti-ble}{adj.}{If you are susceptible to something or someone, you are very likely to be influenced by them.} 
--- \textit{They showed that despite their high accuracies, modern deep
networks are surprisingly \textbf{susceptible} to adversarial attacks
in the form of small perturbations to images that remain
(almost) imperceptible to human vision system.}


